Enriching Object Detection with 2D-3D Registration and Continuous Viewpoint

### 2014-11-14 egpaper_final.tex
Modified table 1, filling out experiment section

We empirically found out that NZ-WHO performs reasonably well without time consuming calibration stage compare to other variational method to generate templates. We used 1 CAD model with viewpoints covering 24 azimuths and 4 elevations. Each template takes approximately 80 milliseconds to generate a NZ-WHO template. We also calibrated templates using the method presented in \cite{Aubry14}. The calibration learns affine transformation of the detection confidence.% Note that in Section \ref{experiments}, we provide the same experiment with 9 CAD models.

\begin{table*}[!htbp]
    \begin{center}
\begin{tabular}{|c|c|c|c|c|}
\hline
Methods &  without Calibration (AP/AVP) & time & w/ Calibration \cite{Aubry14} (AP/AVP) & time \\
\hline\hline
HOG\cite{Dalal05}     & 72.28/48.38  &  31ms  & 60.37/50.19               &   8.7 sec \\ 
WHO-Chol\cite{Hariharan12} &              &3811ms    &                           &   12.4 sec  \\
WHO-GG                & 81.70/74.20  &104ms &     83.714/75.37              &   8.3 sec \\
WHO-CG-Z              & 54.42/49.71  &103ms & \textbf{92.80}/\textbf{81.44} &   8.7 sec  \\
% NZC-WHO-Z    & 89.10/\textbf{78.64} &    & 91.15/74.79                  &     \\
NZ-WHO-CG        & \textbf{90.00}/78.23 & 79ms & 90.31/78.00                   &  8.5 sec   \\
\hline
\end{tabular}
\end{center}
\caption{Average Precision(AP) and Average Viewpoint Precision(AVP) \cite{Xiang14} of variations of WHO on 3DObject Car dataset\cite{Savarese07}. WHO\cite{Hariharan12} whitens all cell, WHO-ZZ whitens all cell then zero out textureless region. NZC-WHO-ZZ first substract mean $\mu$ on non-zero cells and whiten all cells then zero out textureless region. NZ-WHO whitens only non-zero cell. Note that WHO-ZZ got dramatic performance boost after calibration due to strong impact of substracting $\mu$ from all textureless region}
\label{tab:who_initializations}
\end{table*}

@@

In this section, we validate our proposed NZ-WHO templates in two different ways. First, we make a set of NZ-WHO templates for a set of CAD models from various viewpoints. Then we run the bank of NZ-WHO templates as ensembles of weak detectors and show that the rendering image can be We want to see how robust the NZ-WHO to real images a

\subsection{Object Detection} 
Instance-level 2D-3D matching (registration) is a difficult problem since we need a CAD model that looks similar to the object in the image. Especially, due to extreme intraclass variability of chair \cite{Aubry14} used a very large collection of CAD models to cover variety of chairs. Similarly, \cite{Lim14}
\begin{table}[!htbp]
  \begin{center}
    \begin{tabular}{|c|c|c|c|}
    \hline
     AP/MPPE& Ours & ALM\cite{Xiang12} & VOCDPM\cite{Pepik12} \\
    \hline\hline
    car & \textbf{99.8}/91.7 &  98.4/93.4 & \textbf{99.8}/\textbf{97.5} \\ 
    bicycle & 93.0/87.4 & 93.0/91.4 & \textbf{98.8}/\textbf{97.5} \\
    \hline
    \end{tabular}
  \end{center}
  \caption{Average Precision(AP) and Average Viewpoint Accuracy(AVA) on 3DObject dataset. Though we do not need any training images and made templates in few minues, it performs on par with state of the art detectors yet it gives high quality 2D-3D matching.}
  \label{tab:3dobject}
\end{table}

>>>>

We empirically found out that NZ-WHO performs reasonably well without time consuming calibration stage compare to other variational methods to generate templates. We used 1 CAD model with viewpoints covering 24 azimuths and 4 elevations with 250 cells per each template. Each template takes approximately 70 milliseconds to generate a NZ-WHO template. We also calibrated templates using the method presented in \cite{Aubry14}. Briefly, the calibration learns affine transformation of the detection confidence using a set of natural images.% Note that in Section \ref{experiments}, we provide the same experiment with 9 CAD models.

\begin{table*}[!htbp]
    \begin{center}
\begin{tabular}{|c|c|r|c|r|}
\hline
Methods (AP/MPPE) & before calibration  & time & after Calibration \cite{Aubry14} & time \\
\hline\hline
HOG\cite{Dalal05}     & 72.3 / 65.0  &  31ms  & 60.4 / 50.2                 &   8.7 sec \\ 
WHO\cite{Hariharan12} &              &  3811ms&                             &   12.4 sec  \\
WHO-CG                & 81.7 / \texbf{84.9}  &  104ms &     83.7 / 87.3             &   8.3 sec \\
WHO-CG-Z              & 54.4 / 65.1  &  103ms & \textbf{92.8} / 86.7 &   8.7 sec  \\
% NZC-WHO-Z    & 89.10/\textbf{78.64} &    & 91.15/74.79                  &     \\
NZ-WHO-CG        & \textbf{90.0} / 82.8 & 79ms & 90.3 / \textbf{86.8}                   &  8.5 sec   \\
\hline
\end{tabular}
\\\textcolor{red}{TABLE REQUIRES MODIFICATION}
\end{center}
\caption{Average Precision(AP) and Mean Precision in Pose Estimation (MPPE) \cite{Lopez-Sastre11} variations of WHO on 3DObject Car dataset\cite{Savarese07}. WHO refers to standard WHO using the method presented in \cite{Hariharan12}, WHO-CG uses iterative Conjugate Gradient method to generate WHO. WHO-CG-Z uses whiten the whole template and zero out textureless region. NZ-WHO-CG is the NZ-WHO which whitens only non-zero cells using iterative Conjugate Gradient method. The time column indicates the time to generate one template. We followed calibration procedure presented in \cite{Aubry14}.}
\label{tab:who_initializations}
\end{table*}

@@

In this section, we validate our proposed NZ-WHO templates in two different ways. First, we make a set of NZ-WHO templates for a set of CAD models from various viewpoints. Then we run the bank of NZ-WHO templates as an ensemble of weak classifiers and show that our method can work as a standalone detector for simple task. This validates that our ensemble of NZ-WHO templates, though each of templates takes 70ms to generate from a rendering image, can robustly perform 2D-3D matching on real images.

Then, we show that our method can complement  enrich object detection

\subsection{2D-3D Matching as an Object Detector} 
Instance-level 2D-3D matching (registration) is a difficult problem since we need a CAD model that looks similar to the object in the image. Especially, due to extreme intraclass variability of chair \cite{Aubry14} used a very large collection of CAD models to cover variety of chairs. Similarly, \cite{Lim14}
\begin{table}[!htbp]
  \begin{center}
    \begin{tabular}{|c|c|c|c|}
    \hline
     AP/MPPE& Ours & ALM\cite{Xiang12} & VOCDPM\cite{Pepik12} \\
    \hline\hline
    car & \textbf{99.8}/91.7 &  98.4/93.4 & \textbf{99.8}/\textbf{97.5} \\ 
    bicycle & 93.0/87.4 & 93.0/91.4 & \textbf{98.8}/\textbf{97.5} \\
    \hline
    \end{tabular}
  \end{center}
  \caption{Average Precision(AP) and Average Viewpoint Accuracy(AVA) on 3DObject dataset. Though we do not need any training images and made templates in few minues, it performs on par with state of the art detectors yet it gives high quality 2D-3D matching.}
  \label{tab:3dobject}
\end{table}

### 2014-11-14 intro.tex
Modified table 1, filling out experiment section

\begin{figure}[t]
  \centering
  % \includegraphics[width=0.9\linewidth]{schematics} 
  \includegraphics[width=0.99\linewidth]{front} % \\[-5pt]
  % (a)\\[0pt]
  % \setlength\tabcolsep{0pt}
  % \begin{tabular}{cc}
  %     \includegraphics[width=0.45\linewidth]{car/orig2} & 
  %     \includegraphics[width=0.45\linewidth]{car/overlay2}
  %  %   \begin{tabular}{cc}
  %  %       \includegraphics[width=0.16\linewidth]{cad_car/2001-2004 Ford Ranger Edge} & 
  %  %       \includegraphics[width=0.16\linewidth]{cad_car/2002 Dodge Ram FedEx} \\ 
  %  %       \includegraphics[width=0.16\linewidth]{cad_car/2007-Nissan-Versa-_-Tiida-SL} & 
  %  %       \includegraphics[width=0.16\linewidth]{cad_car/2008-Jeep-Cherokee} \\ 
  %  %       \includegraphics[width=0.16\linewidth]{cad_car/2009 Toyota Cargo} & 
  %  %       \includegraphics[width=0.16\linewidth]{cad_car/2010-Chevrolet-Aveo5-LT} \\ 
  %  %       \includegraphics[width=0.16\linewidth]{cad_car/2012-Citroen-DS4}  
  %  %   \end{tabular}
  % \end{tabular}\\
  % (b)
  \caption{Using a bank of CAD models, we generate NZ-WHO templates which can be used to either detect objects directly or initialize pose of an object in the bounding box from other detectors. Once initialization is given, we use NZ-WHO to propose and validate plausible pose on-the-fly and further tune the translation, 3D viewpoint and focal length continuously.}
  % \vspace{-1em}
  \label{fig:front}
\end{figure}

@@

In this paper, we propose a novel method for 2D-3D alignment of
exemplar CAD models to real-world images that circumvents the need for
calibration, and greatly enhances the scalability of E-LDA. As a
result, we can render novel views and train corresponding exemplar
models {\em on the fly}, without the need for offline processing. As a
by-product, we can formulate the alignment problem as a parameter
search in a continuos pose space, consisting of azimuth, elevation,
and ~\scream{}, resulting in truely continuous pose estimates, which
we implement using MCMC sampling.
%  require a large number of rendering and 2D
% templates for each of the CAD model with specific viewpoint. Since
% there are so many templates that it becomes almost impossible to get
% all the true positive image from training data. Instead \cite{Aubry14,
%   Lim14} used whitening as a preprocessing stage \cite{Hariharan12} to
% make templates more discriminative. Then calibration is done on a
% small training dataset.
%
% Although whitening to create template is faster than some of
% instance-level matching algorithms such as training Exemplar-SVM
% \cite{Malisiewicz11} or complicated models such as LEVAN
% \cite{Divvala14}, whitening and calibration large number of templates
% takes very long time. Also, once the fixed discrete viewpoint
% templates have been made and calibrated, it is difficult to fine-tune
% the prediction made using the large collection of templates.

>>>>

\begin{figure}[t]
  \centering
  % \includegraphics[width=0.9\linewidth]{schematics} 
  \includegraphics[width=0.99\linewidth]{front} % \\[-5pt]
  % (a)\\[0pt]
  % \setlength\tabcolsep{0pt}
  % \begin{tabular}{cc}
  %     \includegraphics[width=0.45\linewidth]{car/orig2} & 
  %     \includegraphics[width=0.45\linewidth]{car/overlay2}
  %  %   \begin{tabular}{cc}
  %  %       \includegraphics[width=0.16\linewidth]{cad_car/2001-2004 Ford Ranger Edge} & 
  %  %       \includegraphics[width=0.16\linewidth]{cad_car/2002 Dodge Ram FedEx} \\ 
  %  %       \includegraphics[width=0.16\linewidth]{cad_car/2007-Nissan-Versa-_-Tiida-SL} & 
  %  %       \includegraphics[width=0.16\linewidth]{cad_car/2008-Jeep-Cherokee} \\ 
  %  %       \includegraphics[width=0.16\linewidth]{cad_car/2009 Toyota Cargo} & 
  %  %       \includegraphics[width=0.16\linewidth]{cad_car/2010-Chevrolet-Aveo5-LT} \\ 
  %  %       \includegraphics[width=0.16\linewidth]{cad_car/2012-Citroen-DS4}  
  %  %   \end{tabular}
  % \end{tabular}\\
  % (b)
  \caption{Using a bank of CAD models, we generate NZ-WHO templates which can be used to either detecting objects directly or initializing pose of an object in the bounding box from other detectors. Once the initialization is given, we use NZ-WHO to propose and validate plausible pose on-the-fly and further tune the translation, 3D viewpoint and focal length continuously.}
  % \vspace{-1em}
  \label{fig:front}
\end{figure}

@@

In this paper, we propose a novel method for 2D-3D alignment of
exemplar CAD models to real-world images that circumvents the need for
calibration, and greatly enhances the scalability of E-LDA. As a
result, we can render novel views and train corresponding exemplar
models {\em on the fly}, without the need for offline processing. As a
by-product, we can formulate the alignment problem as a parameter
search in a continuos pose space, consisting of yaw, pitch and roll, resulting in truely continuous pose estimates, which
we implement using MCMC sampling.
%  require a large number of rendering and 2D
% templates for each of the CAD model with specific viewpoint. Since
% there are so many templates that it becomes almost impossible to get
% all the true positive image from training data. Instead \cite{Aubry14,
%   Lim14} used whitening as a preprocessing stage \cite{Hariharan12} to
% make templates more discriminative. Then calibration is done on a
% small training dataset.
%
% Although whitening to create template is faster than some of
% instance-level matching algorithms such as training Exemplar-SVM
% \cite{Malisiewicz11} or complicated models such as LEVAN
% \cite{Divvala14}, whitening and calibration large number of templates
% takes very long time. Also, once the fixed discrete viewpoint
% templates have been made and calibrated, it is difficult to fine-tune
% the prediction made using the large collection of templates.
